### 2023-07-01 Text/Poster/poster_Igarss_23.tex
QR code added to poster

\title{%
  \texorpdfstring{%
    \makebox[\linewidth]{	%
      \makebox[100pt][l]{%
        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          {\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}% Left logo
      }\hfill
			\makebox[\dimexpr\linewidth-4em][c]{%
        \begin{minipage}{\linewidth}
          \centering
          \LARGE QUALITY ASSESSMENT MEASURES FOR EXPLAINABLE FUSION OF STATISTICAL\\ EVIDENCES OF EDGES IN POLSAR IMAGES: A FIRST APPROACH
        \end{minipage}
      }%

      \hfill\makebox[-50pt][r]{%
        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          {\includegraphics[height=3.0\baselineskip]{figures/logos.pdf}}% Right logo
      }%
    }%
  }
  } % Poster title

	\author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
\institute[]{$^1$Universidade Federal de Pernambuco, Recife, Brazil\\
$^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
$^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}

>>>>

\title{%
  \texorpdfstring{%
    \makebox[\linewidth]{%
      \makebox[-200pt][l]{%
        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          {\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}}% Left logo
      \hfill
      \makebox[\dimexpr\linewidth-4em][c]{%
        \begin{minipage}{\linewidth}
          \centering
          \LARGE QUALITY ASSESSMENT MEASURES FOR EXPLAINABLE FUSION OF STATISTICAL\\ EVIDENCES OF EDGES IN POLSAR IMAGES: A FIRST APPROACH
        \end{minipage}
      }%
      \hfill\hspace{-50cm} %
      \raisebox{\dimexpr-\height-1.1\baselineskip}[0pt][0pt] % 
        {\includegraphics[height=2.9\baselineskip]{../../Figures/PNG/QRCode-WebPageVUW.png}}% New figure
      \hfill
      \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
        {\includegraphics[height=3.0\baselineskip]{figures/logos.pdf}}% Right logo
    }%
  }%
}

\author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
\institute[]{%
  \makebox[\linewidth]{%
    \begin{minipage}[c]{0.6\linewidth}
      \centering
      \vspace{0.5cm}
      $^1$Universidade Federal de Pernambuco, Recife, Brazil\\
      $^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
      $^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand
    \end{minipage}%

}}

%\title{%
  %\texorpdfstring{%
    %\makebox[\linewidth]{	%
      %\makebox[-100pt][l]{%
        %\raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          %{\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}% Left logo
      %}\hfill
			%\makebox[\dimexpr\linewidth-4em][c]{%
        %\begin{minipage}{\linewidth}
          %\centering
          %\LARGE QUALITY ASSESSMENT MEASURES FOR EXPLAINABLE FUSION OF STATISTICAL\\ EVIDENCES OF EDGES IN POLSAR IMAGES: A FIRST APPROACH
        %\end{minipage}
      %}%
      %\hfill\hspace{-20cm} % Ajusta la cantidad de espacio según tus necesidades
      %\raisebox{\dimexpr-\height-1.5\baselineskip}[0pt][0pt] % Ajusta la cantidad de espacio según tus necesidades
        %{\includegraphics[height=2.7\baselineskip]{../../Figures/PNG/QRCode-WebPageVUW.png}}% New logo
            %\hfill\makebox[-50pt][r]{%
        %\raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          %{\includegraphics[height=3.0\baselineskip]{figures/logos.pdf}}% Right logo
      %}%
    %}%
  %}
  %} % Poster title
	%
	%\author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
%\institute[]{$^1$Universidade Federal de Pernambuco, Recife, Brazil\\
%$^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
%$^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
